\boldmath Heavy resonances at energy frontier colliders

### 2019-02-08 paper.tex
Updates from Overleaf

\begin{figure}[!htb]
  \centering
%  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/mzp_sel0_nostack_log_mm.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle.eps}
  \caption{Left: Invariant mass for a 30\,TeV signal after full event selection for the $\mu\mu$ channel. Middle: 95\% CL limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel. Right: integrated luminosity versus mass for a $5\sigma$ discovery comparing ee, $\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:ll}
\end{figure}

@@

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mt_finalsel_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs_fullmt.eps}
 % \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs_mt_4TeVmzp.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle_fullmt.eps}
%  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle_mt_4TeVmzp.eps}
  \caption{Left: Di-$\tau$ transverse mass for a 10\,TeV signal after full event selection. Middle: 95\% CL limit versus mass. Right: integrated luminosity versus mass for a $5\sigma$ discovery.}
  \label{figure:leptonicresonances:tautau}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf04_sel1_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Qstar_jj_fcc_v02.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_jj_rootStyle.eps}
   \caption{Invariant mass distribution of the two selected jets for a 40\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:jj}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_MetCorr_fit_sel8_nostack_log.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tt_fcc_v02.eps}
   \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tt_SSM_TC2_tagger_TRFbtag_rootStyle.eps}
  \caption{Invariant mass distribution of the two selected top-jets (left) for a 20\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:tt}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_fit_sel4_nostack_log.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_RSGraviton_ww_fcc_v02.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ww_tagger_rootStyle.eps}
  \caption{Invariant mass distribution of the two selected W-jets for a 20\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:ww}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with 27 TeV HE-LHC}
\label{sec:ana27tev}
The search for heavy resonances have also been study at the 27\,TeV HE-LHC. The analyses strategies remains identical to what was already presented in the previous sections, the only differences are re-optimisation of some selection thresholds to accommodate for the lower center of mass energy. The changes can be summarised as follows:
\begin{itemize}
\item \Zpee\ and \Zpmumu : lepton $p_T$ lowered from 1 to 0.5\,TeV
%\item \Zpmumu\ f.a. and t-channel LQ : leton $p_T$ lowered from  1.2 TeV to 0.75 TeV
\item \Zptata\ : mass dependent cuts changed as shown in Table~\ref{tab:leptonicresonances:tautau27}
\item \rsg, \Zptt, \qjj\ : jet $p_T$ lowered from 3 to 1\,TeV
\end{itemize}
The results are summarised in Table~\ref{tab:27vs100}, together with a comparison to FCC-hh and Figure~\ref{figure:resonances:summary}.

@@

\begin{table}[!htb]\centering
\begin{tabular}{|l|c|c|c|}
\hline
analysis   & \multicolumn{3}{c|}{HE-LHC (FCC-hh)} \\
           & Limit [TeV] & Disco [TeV]   & Disco [TeV] \\
           &  15 (30) ab$^{-1}$ & 1 (2.5) ab$^{-1}$ & 15 (30) ab$^{-1}$ \\
\hline
\Zpll\ (l=e,$\mu$) & 13 (40) & 10 (33) & 13 (43) \\
\Zptata       &  6 (14) &  3 (12) &  6 (18) \\
%\Zpmumu\ f.a. &  4 (25) &  - (10) &  2 (19) \\
\Zptt         & 10 (28) &  6 (16) &  8 (23) \\
\rsg          &  8 (28) &  5 (15) &  7 (22) \\
\qjj          & 14 (43) & 10 (36) & 12 (40) \\
\hline
\end{tabular}
\caption{95\% CL limits and 5$\sigma$ discovery reach comparison between HE-LHC and FCC-hh. The numbers in parenthesis are the FCC numbers. \CH{TO BE REMOVED if decide that summary plots are better}}
\label{tab:27vs100}
\end{table}

@@

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.30\columnwidth]{Fig/ry_afb_200GeV_eta2p5_interf.eps}
   \includegraphics[width=0.30\columnwidth]{Fig/sigma_vs_lumi.eps}
   \includegraphics[width=0.30\columnwidth]{Fig/Zp_branching_6TeV_15ab.eps}
  \caption{Left: Scatter plot of $r_y$ versus $A_{FB}$ with 200~GeV and mass window. The full interference is included. Center: Fitted signal cross-section together with its corresponding error versus integrated luminosity. Right: Fitted cross-section of the three hadronic analyses. Statistical and full uncertainties are shown on each point.}
  \label{fig:ana:res}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mzp_sel0_nostack_log_FA.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_mumu_fcc_v02_FA.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_mumu_rootStyle_FA.pdf}
  \caption{Left : Invariant mass for a 30~TeV signal after full event selection in flavour anomaly scenario. Limit versus mass (middle) and luminosity for a $5\sigma$ discovery (right). }
  \label{figure:leptonicresonances:resultsmumu_flav}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
    \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_Zp_jj_comb_smeared_rootStyle.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ll_smearhl_rootStyle.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_zprime_tt_smeared.pdf}
  \caption{Left : Invariant mass for a 30~TeV signal after full event selection in flavour anomaly scenario. Limit versus mass (middle) and luminosity for a $5\sigma$ discovery (right). \CH{Plots still need edits}}
  \label{figure:detperf}
\end{figure}

@@

\begin{figure}[!htbp]\centering
\includegraphics[width=0.3\textwidth]{Fig/TMVA/Jet1_Flow15_sel0_nostack_logx.eps}
\includegraphics[width=0.3\textwidth]{Fig/TMVA/Jet1_tau32_sel0_nostack_log.eps}
\includegraphics[width=0.3\textwidth]{Fig/TMVA/effQCD_vs_effWhadBlue_thadRed_log.pdf}
\caption{Left: Energy-flow ($E_{F}(1,0.05)$) observable for W and QCD jets. Middle: ($\tau_(3,2)$) observable for t and QCD jets. Right: Light jet rejection versus tagging efficiency for the $W$ tagger (blue) and top tagger (red) -> re-do on-going.}
\label{fig:TMVA_final_result}
\end{figure}

@@

\begin{figure}[!htb]\centering
\includegraphics[width=0.45\columnwidth]{Fig/Zptt/Mj1j2_pf08_MetCorr_sel8_nostack_log.eps}
\includegraphics[width=0.45\columnwidth]{Fig/Zptt/Zptt_QCD_sel8_Mj1j2_pf08_MetCorr_fit.eps}
\caption{Invariant mass prior to fit.}
\label{fig:hadronicresonances_nofit}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%appendix
\section{More information on analyses}
\label{app:anamore}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_ee_fcc_v02_allxs.eps}
  \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_mumu_fcc_v02_allxs.eps}
  \caption{Limit versus mass for the ee channel (left) and $\mu\mu$ channel (right) for an integrated luminosity of $30$\,ab$^{-1}$. }
  \label{figure:leptonicresonances:resultseemumu}
\end{figure}

@@

>>>>

\begin{figure}[!htb]
  \centering
%  \includegraphics[width=0.35\columnwidth]{Fig/mzp_sel0_nostack_log_ee.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/mzp_sel0_nostack_log_mm-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_ll_fcc_v02_allxs-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ll_comb_rootStyle-eps-converted-to.pdf}
  \caption{Left: Invariant mass for a 30\,TeV signal after full event selection for the $\mu\mu$ channel. Middle: 95\% CL limit versus mass for the combined di-lepton ($ee$, $\mu\mu$) channel. Right: integrated luminosity versus mass for a $5\sigma$ discovery comparing ee, $\mu\mu$ and combined channels.}
  \label{figure:leptonicresonances:ll}
\end{figure}

@@

\begin{figure}[htb!]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mt_finalsel_nostack_log-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs_fullmt-eps-converted-to.pdf}
 % \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tautau_fcc_v02_allxs_mt_4TeVmzp.eps}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle_fullmt-eps-converted-to.pdf}
%  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tautau_rootStyle_mt_4TeVmzp.eps}
  \caption{Left: Di-$\tau$ transverse mass for a 10\,TeV signal after full event selection. Middle: 95\% CL limit versus mass. Right: integrated luminosity versus mass for a $5\sigma$ discovery.}
  \label{figure:leptonicresonances:tautau}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf04_sel1_nostack_log-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Qstar_jj_fcc_v02-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_jj_rootStyle-eps-converted-to.pdf}
   \caption{Invariant mass distribution of the two selected jets for a 40\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:jj}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_MetCorr_fit_sel8_nostack_log-eps-converted-to.pdf}
   \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_tt_fcc_v02-eps-converted-to.pdf}
   \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tt_SSM_TC2_tagger_TRFbtag_rootStyle-eps-converted-to.pdf}
  \caption{Invariant mass distribution of the two selected top-jets (left) for a 20\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:tt}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/Mj1j2_pf08_fit_sel4_nostack_log-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_RSGraviton_ww_fcc_v02-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ww_tagger_rootStyle-eps-converted-to.pdf}
  \caption{Invariant mass distribution of the two selected W-jets for a 20\,TeV signal (left), 95\% CL limit versus mass (middle) and $5\sigma$ discovery reach (right).}
  \label{figure:hadronicresonances:ww}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Comparison with 27 TeV HE-LHC}
\label{sec:ana27tev}
The search for heavy resonances have also been study at the 27\,TeV HE-LHC. The analyses strategies remains identical to what was already presented in the previous sections, the only differences are re-optimisation of some selection thresholds to accommodate for the lower center of mass energy. The changes can be summarised as follows:
\begin{itemize}
\item \Zpee\ and \Zpmumu : lepton $p_T$ lowered from 1 to 0.5\,TeV
%\item \Zpmumu\ f.a. and t-channel LQ : leton $p_T$ lowered from  1.2 TeV to 0.75 TeV
\item \Zptata\ : mass dependent cuts changed as shown in Table~\ref{tab:leptonicresonances:tautau27}
\item \rsg, \Zptt, \qjj\ : jet $p_T$ lowered from 3 to 1\,TeV
\end{itemize}
The results are summarised in Figure~\ref{figure:resonances:summary}, together with a comparison to FCC-hh for the 95\% CL (left) and 5$\sigma$ discovery reach (right).

@@

%\begin{table}[!htb]\centering
%\begin{tabular}{|l|c|c|c|}
%\hline
%analysis   & \multicolumn{3}{c|}{HE-LHC (FCC-hh)} \\
%           & Limit [TeV] & Disco [TeV]   & Disco [TeV] \\
%           &  15 (30) ab$^{-1}$ & 1 (2.5) ab$^{-1}$ & 15 (30) ab$^{-1}$ \\
%\hline
%\Zpll\ (l=e,$\mu$) & 13 (40) & 10 (33) & 13 (43) \\
%\Zptata       &  6 (14) &  3 (12) &  6 (18) \\
%%\Zpmumu\ f.a. &  4 (25) &  - (10) &  2 (19) \\
%\Zptt         & 10 (28) &  6 (16) &  8 (23) \\
%\rsg          &  8 (28) &  5 (15) &  7 (22) \\
%\qjj          & 14 (43) & 10 (36) & 12 (40) \\
%\hline
%\end{tabular}
%\caption{95\% CL limits and 5$\sigma$ discovery reach comparison between HE-LHC and FCC-hh. The numbers in parenthesis are the FCC numbers. \CH{TO BE REMOVED if decide that summary plots are better}}
%\label{tab:27vs100}
%\end{table}

@@

\begin{figure}[!htb]
  \centering
   \includegraphics[width=0.30\columnwidth]{Fig/ry_afb_200GeV_eta2p5_interf-eps-converted-to.pdf}
   \includegraphics[width=0.30\columnwidth]{Fig/sigma_vs_lumi-eps-converted-to.pdf}
   \includegraphics[width=0.30\columnwidth]{Fig/Zp_branching_6TeV_15ab-eps-converted-to.pdf}
  \caption{Left: Scatter plot of $r_y$ versus $A_{FB}$ with 200~GeV and mass window. The full interference is included. Center: Fitted signal cross-section together with its corresponding error versus integrated luminosity. Right: Fitted cross-section of the three hadronic analyses. Statistical and full uncertainties are shown on each point.}
  \label{fig:ana:res}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.32\columnwidth]{Fig/mzp_sel0_nostack_log_FA-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/lim_Zprime_mumu_ano_fcc_v02-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_mumu_ano_rootStyle-eps-converted-to.pdf}
  \caption{Left : Invariant mass for a 30~TeV signal after full event selection in flavour anomaly scenario. Limit versus mass (middle) and luminosity for a $5\sigma$ discovery (right). }
  \label{figure:leptonicresonances:resultsmumu_flav}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
    \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_Zp_jj_comb_smeared_rootStyle-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_ll_smearhl_rootStyle-eps-converted-to.pdf}
  \includegraphics[width=0.32\columnwidth]{Fig/DiscoveryPotential_tt_TC2_tagger_TRFbtag_degrade_rootStyle-eps-converted-to.pdf}
  \caption{Left : Invariant mass for a 30~TeV signal after full event selection in flavour anomaly scenario. Limit versus mass (middle) and luminosity for a $5\sigma$ discovery (right). }
  \label{figure:detperf}
\end{figure}

@@

\begin{figure}[!htbp]\centering
\includegraphics[width=0.3\textwidth]{Fig/TMVA/Jet1_Flow15_sel0_nostack_logx-eps-converted-to.pdf}
\includegraphics[width=0.3\textwidth]{Fig/TMVA/Jet1_tau32_sel0_nostack_log-eps-converted-to.pdf}
\includegraphics[width=0.3\textwidth]{Fig/TMVA/effQCD_vs_effWhadBlue_thadRed_log.pdf}
\caption{Left: Energy-flow ($E_{F}(1,0.05)$) observable for W and QCD jets. Middle: ($\tau_(3,2)$) observable for t and QCD jets. Right: Light jet rejection versus tagging efficiency for the $W$ tagger (blue) and top tagger (red) -> re-do on-going.}
\label{fig:TMVA_final_result}
\end{figure}

@@

\begin{figure}[!htb]\centering
\includegraphics[width=0.45\columnwidth]{Fig/Zptt/Mj1j2_pf08_MetCorr_sel8_nostack_log-eps-converted-to.pdf}
\includegraphics[width=0.45\columnwidth]{Fig/Zptt/Zptt_QCD_sel8_Mj1j2_pf08_MetCorr_fit-eps-converted-to.pdf}
\caption{Invariant mass prior to fit.}
\label{fig:hadronicresonances_nofit}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%appendix
\section{More information on analyses}
\label{app:anamore}
\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_ee_fcc_v02_allxs-eps-converted-to.pdf}
  \includegraphics[width=0.35\columnwidth]{Fig/lim_Zprime_mumu_fcc_v02_allxs-eps-converted-to.pdf}
  \caption{Limit versus mass for the ee channel (left) and $\mu\mu$ channel (right) for an integrated luminosity of $30$\,ab$^{-1}$. }
  \label{figure:leptonicresonances:resultseemumu}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.49\columnwidth]{Fig/summaryLimit_onlyFCChh.pdf}
  \includegraphics[width=0.49\columnwidth]{Fig/summaryLimit_onlyHELHC.pdf}
  \caption{Summary of the 95\% CL limits as a function of the resonance mass for different luminosity scenario of FCC-hh and HE-LHC.}
  \label{figure:resonances100:summarylimit}
\end{figure}
